Adaptive Sequential Model Selection

### 2015-07-19 paper.tex
rob added larexample.pdf

To choose a model we feed the resulting $p$-values as inputs into sequential stopping rules proposed by \citet{gsell2013sequential} and \citet{li2015accumulation}, achieving adaptive control of the familywise error rate or false discovery rate. These stopping rules assume that the single-step null $p$-values are independent of each other and of the non-null $p$-values, a condition that is not satisfied by the $p$-values of \citet{taylor2014exact}. We derive intuitive and general conditions for independence and show that our proposed constructions yield independent $p$-values.
\end{abstract}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline\\
 Step& Predictor& Naive pvalue& Saturated pvalue& Max-t pvalue\cr
  \hline\\
1 & 3& 0.00 & 0.00 & 0.00 \\ 
  2 & 9 & 0.00 & 0.00 & 0.00 \\ 
  3 & 4 & 0.00 & \color{red}{0.05} & 0.00 \\ 
  4 & 20 & 0.00 & 0.33 & 0.01 \\ 
  5 & 37 & 0.00 & 0.76 & 0.05 \\ 
  6 & 7 & 0.00 & 0.25 & 0.05 \\ 
  7 & 2 & 0.00 & 0.00 & 0.00 \\ 
  8 & 19 & 0.02 & 0.03 & \color{red}{0.37} \\ 
  9 & 11 & 0.11 & 0.55 & 0.95 \\ 
  10 & 52 & 0.21 & 0.91 & 0.92 \\ 
  11 & 57 & 0.05 & 0.37 & 0.21 \\ 
  12 & 24 & 0.22 & 0.15 & 0.00 \\ 
  13 & 5 & 0.18 & 0.07 & 0.10 \\ 
  14 & 49 & 0.16 & 0.97 & 0.75 \\ 
  15 & 30& 0.21 & 0.15 & 0.05 \\ 
  16 & 46 & \color{red}{0.16} & 0.05 & 0.53 \\ 
  17 & 59 & 0.27 & 0.45 & 0.68 \\ 
  18 & 33 & 0.12 & 0.71 & 0.80 \\ 
  19 & 62 & 0.08 & 0.40 & 0.48 \\ 
  20 & 27 & 0.17 & 0.60 & 0.50 \\ 
   \hline\\
\end{tabular}
\caption{Rob's data}
\end{table}

>>>>

To choose a model we feed the resulting $p$-values as inputs into sequential stopping rules proposed by \citet{gsell2013sequential} and \citet{li2015accumulation}, achieving adaptive control of the familywise error rate or false discovery rate. These stopping rules assume that the single-step null $p$-values are independent of each other and of the non-null $p$-values, a condition that bmiis not satisfied by the $p$-values of \citet{taylor2014exact}. We derive intuitive and general conditions for independence and show that our proposed constructions yield independent $p$-values.
\end{abstract}

@@
